Provenance analysis

### 2021-07-26 analysis/provenance2.Rmd
Provenances in number of calls

---
title: "Provenance analysis"
author: "Pierre Donat-Bouillud"
output:
  html_document:
        gallery: false
        toc: true
        toc_depth: 3
        toc_float: true
        df_print: paged
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  base_dir: Data/package/
  calls_path: summarized.fst
  corpus_path: corpus.txt
  static_path: evals-static.csv
  force_rebuild: FALSE
---

@@

# Tags will be prefixed by the dataset name
create_tags(path(TAGS_DIR, paste0(dataset_name, "_provenance.tex")), prefix = dataset_name, default = TRUE)
# Also use ggsave_prefix instead of ggsave if you need to save a graph

@@

lock_path <- paste0(params$base_dir, ".provenance-lock.fst")
min_path <- paste0(params$base_dir, "Eprov.fst")

@@

  E_raw %>% select(
    run_package = package, #      The package which was run to trigger the eval
    ev_variant = eval_function, # Which eval variant was called
    duplicates = nb_ev_calls, #   Number of identical eval calls (weight)
    src_ref = eval_call_srcref, # Source ref for the eval call site
    file, #                       Script file name (name of this run)
    ev_package = eval_source, #   Package of the call site
    type = expr_resolved_type_tag, #   Argument type
    ev_call = eval_call_expression,
    ev_expr = expr_expression,
    caller_expression,
    match_call = expr_match_call,
    parsed = expr_parsed_expression,
  ) -> E_prov

  E_prov %>% write_fst(min_path)
  sz <- file.size(calls_path) %>% as_tibble()
  write.fst(sz, lock_path)
}

@@

>>>>

---
title: "Provenance analysis"
author: "Pierre Donat-Bouillud"
output:
  html_document:
        gallery: false
        toc: true
        toc_depth: 3
        toc_float: true
        df_print: paged
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  #base_dir: Data/package/
  base_dir: /mnt/ocfs_vol_00/project-evalr/evalr-experiment/run/preprocess/package/
  calls_path: summarized.fst
  corpus_path: corpus.txt
  static_path: evals-static.csv
  force_rebuild: FALSE
---

@@

# Tags will be prefixed by the dataset name
create_tags(path(TAGS_DIR, paste0(dataset_name, "_provenance2.tex")), prefix = dataset_name, default = TRUE)
# Also use ggsave_prefix instead of ggsave if you need to save a graph

@@

lock_path <- paste0(params$base_dir, ".provenance2-lock.fst")
min_path <- paste0(params$base_dir, "Eprov2.fst")

@@

  E_raw %>% select(
    run_package = package, #      The package which was run to trigger the eval
    ev_variant = eval_function, # Which eval variant was called
    duplicates = nb_ev_calls, #   Number of identical eval calls (weight)
    src_ref = eval_call_srcref, # Source ref for the eval call site
    file, #                       Script file name (name of this run)
    ev_package = eval_source, #   Package of the call site
    type = expr_resolved_type_tag, #   Argument type
    ev_call = eval_call_expression,
    ev_expr = expr_expression,
    caller_expression,
    provenance, # the main provenance (i.e. climbing up LHSs)
    provenance_args,
    nb_provenances,
    nb_operations,
    longest_path_size,
    all_provenances
  ) -> E_prov

  #E_prov %>% write_fst(min_path)
  sz <- file.size(calls_path) %>% as_tibble()
  #write.fst(sz, lock_path)
}

@@

In the dataset, the `provenance` column refers to the main provenance of an expression passed to `eval`. It is obtained by traversing the provenance graph and following the LHSs.

# Provenance in numbers of calls

```{r}
provenance_calls <- E_prov %>% count(provenance, wt = duplicates, sort = TRUE) %>% 
  mutate(pc = 100 * n / sum(n), cpc = cumsum(pc))

nrows <- min(10, nrow(provenance_calls))
r_vec("nb provenance calls", nrows, provenance_calls$provenance)
r_vec("percent provenance calls", nrows, provenance_calls$pc)
r_vec("cumpercent provenance calls", nrows, provenance_calls$cpc)
```

`r datatable(provenance_calls)`

# Provenance in number of sites

# All provenances

## By combinations

## In absolute numbers
